---
title: "introduction"
#output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{The EDClust User's Guide}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
output:
  BiocStyle::html_document:
    toc_float: FALSE
---


\tableofContents

# Introduction

High-throughput technologies have revolutionized 
the genomics research.  The early
applications of the technologies were largely on 
cell lines. However, there is an increasing number 
of larger-scale, population level clinical studies 
in recent years, hoping to identify diagnostic 
biomarkers and therapeutic targets.  The samples 
collected in these studies, such as blood, tumor, 
or brain tissue, are mixtures of a number of different
cell types.  The sample mixing complicates data analysis
because the experimental data from the high-throughput 
experiments are weighted averages of signals from multiple
cell types. For these data, traditional analysis methods that ignores
the cell mixture 
will lead to results with low resolution,  biased, or
even errorneous results. 
For example, it has been discovered that in epigenome-wide 
association studies (EWAS), the mixing proportions 
can be confounded with the experimental factor of 
interest (such as age). Ignoring the cell mixing 
will lead to  false positives. 
On the other hand, cell type specific changes 
under different conditions could be associated
with disease pathogenesis and progressions, which are of
great interests to researchers.

For heterogeneous samples, it is possible to profile the
pure cell types through experimental techniques.
They are, however, laborious and expensive that cannot
be applied to large scale studies.
Computational tools for analzying the mixed data have been developed 
for proportion estimation and cell type 
specific signal detection. 
<!-- deconvolution of signals and detection of signals.  -->
<!-- Without the experimental tools,  -->
There are two fundamental questions in this type of analyses: 
<!-- that are  for conducting in-silico 
deconvolution of signals and detection of signals.  -->

1. How to estimate mixing proportions?  


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(EDClust)
```
